\section{Key Stakeholders}

\subsection{Merchants}
The major benefits that the merchants will receive from this application is to 
increase it reach to more costumers, will also save cost because they wouldn't 
need to hire a delivery service nor there is a need to keep maintenance of 
the vehicles.\newline

\noindent The application will increase the merchants sales, since this is 
another sales channel besides their current workflow.\newline

\noindent Once of the major features is that the application will provide 
the merchant a delivery service, a bigger pool of costumers while also 
enables insights on what costumers are purchasing not only in their stores 
but the market in general, giving them information on what items to promote.

\subsection{Costumers}

The major benefits for costumers is that they will be able to 
find out places near their home from where they can purchase, since the 
merchants that get display are close to the costumers, the delivery time is
going low.\newline

\noindent Costumers also avoid spending time going to the stores, doing the 
line and purchasing the items, they only need to make the order and they 
get it delivered at their doorstep in less than 2 hours.

\subsection{Drivers}

The main benefit for the drivers is to get another source of income by using 
their current means of transportation as an asset. For them one of the major 
features is going to display in the map the play where they need to do the 
shopping and the location where they need to deliver. \newline

\noindent They also require to keep track of the milage and time of the order, 
and also keep track of all the orders that were perform by the drivers.