\section{Dictionary}
\begin{packed_dict}
	\item \textbf{Stream}: Content sent over a compress form over the internet 
	and displayed to a viewer in real time.
	\begin{itemize}
		\item \textbf{Live stream}: The content is transmitted at the same time 
		(or with low latency) from when is recorded.
		\item \textbf{Recorded Stream}: The content is previously recorded 
		and get played by the viewers on demand.
	\end{itemize}
	\item \textbf{Picture-in-Picture (PiP)}: One content is displayed full 
	screen while other content gets displayed in inset windows.
	\item \textbf{Multi-track}: Multiple, separate streams of sound without 
	defined locations in a sound field
	\item \textbf{Instant Replay}: Immediate playback of a main broadcast. 
	Usually in slow motion.
	\item \textbf{Play Breakdown}: An in-depth discussion about a particular 
	play.
	\item \textbf{Overlay effects}: Is when the main broadcast gets dimmed 
	out and a particular effect appears on top usually to highlight a 
	particular area.
	\item \textbf{Multicam}: Method of filmmaking where multiple cameras 
	record the same subject but from multiple angles
	\item \textbf{Single camera setup}: Method of filmmaking where a single 
	camera records the subject from one particular angle.
	\item \textbf{Embed}: Particular piece of software that is bound to 
	another piece of software.
	\item \textbf{Encoding}: Process of converting data into a specific 
	format.
	\item \textbf{Decoding}: Process of converting an encoded data into its 
	original sequence or data.
	\item \textbf{ShadowPlay}: Program that keeps recording from the last 
	five minutes from the current time. This is a product from Nvidia.
	\item \textbf{HLS}: Live stream protocol that runs over http which 
	provide adaptive bitrate streaming originally developed by Apple.
	\item \textbf{Multi-source stream}: Mixed stream that gets created 
	by using multiple streams as the source.
	\item \textbf{Split-screen}: When a particular window gets divided into 
	two sections and each one displays a different stream.
	\item \textbf{WebRTC}: HTML5 specification that enables real time media 
	functionalities between browser and devices.
	\item \textbf{Localization}: Process of adapting a product's translation 
	to a specific country or region. 
\end{packed_dict}





















