\documentclass[12pt]{article}
\usepackage[a4paper,
	bindingoffset=0.2in,%
        left=1.2in,
        right=1.2in,
        top=1in,
        bottom=1in,%
        footskip=.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{xltxtra,fontspec,xunicode}
\setromanfont[Numbers=Uppercase]{Inter}
\defaultfontfeatures{Scale=MatchLowercase}

{
\fontfamily{lmss}\selectfont 

%opening
\title{
    Project Proposal \\ 
    \small Team 4
}

\author{
    Thomas Ripp
    \and 
    Joseph Mirabile
    \and 
    Jose Cruz
}

\date{
    Stevens Institute of Technology \\
    \small\today
} 

\begin{document}
\maketitle
\tableofcontents
\pagebreak
}

\section{Bidding platform for freelancers}
\subsection{Context}
A lot of people have tasks that they would like to perform but either they are 
too busy or too lazy to do them. The goal of this project is to create a 
platform where people can submit tasks or projects they want and how much 
they are willing to pay for it.\newline

Other people can bid on how much they are willing to be paid to perform that 
task, then the person who posts the task is going to choose a person from the 
people who bid and that person is going to do the task.

\subsection{Purpose}
Enable people to outsource their tasks, chores or projects.

\subsection{Business value}
People  who  post  the  project  could  get  a  cheaper  option  since  there  
is competition, and people who have the time and skills are able to make some 
money, and as a hosting platform we charge a fee for posting the job and 
a service fee for every transaction.

\pagebreak

\section{Activity Finder}
\subsection{Context}
Used for when someone doesn’t know what to do or what’s nearby when they’re 
bored. Home alone and want to get out of the house or simply out of plans for 
a hang out with friends. 

\subsection{Purpose}
Uses maps to locate nearby area for fun attractions such as rock climbing 
or arcades. Can be filtered for specific interests.

\subsection{Business value}
Companies found through the application would pay a fee to post content or 
activities in the app. Enables users to purchase items or promotions from 
businesses through the app.

\pagebreak

\section{Courier Service App}
\subsection{Context}
You have a small package that you want to send to someone, whether it be your 
friend’s jacket you borrowed or documents that your coworker needs to get. 
However, you are too busy or cannot be bothered to deliver these items 
personally. \newline

That is when you request a courier service in your area to deliver 
these items at a proportional rate to the distance the package must travel, 
within reason. 

\subsection{Purpose}
Enable people to send packages without the need to fill out a form, wait 
inline or go to a specific place to send a package nearby.

\subsection{Business value}
We outsource the labor to available individuals who want to make extra 
money and the platform collects a percentage of the rate for each transaction. 

\end{document}