\section{Quality Attributes}
\subsection{Availability}
\begin{enumerate}[label=AVL-\arabic*]
    \item The PSSS shall be available at least 99.9\% during holidays, 
    from 01:00 AM to 23:59 PM
    \item The PSSS shall be available at least 99\% during the day on regular 
    days (days that are not holidays), from 9:00 AM to 7:00 PM.
    \item The PSSS shall be available at least 90\% during 
    the night on regular days (days that are not holidays), from 
    01:00AM to 8:59 AM and from 7:01 PM to 11:59 PM.
\end{enumerate}

\subsection{Installability}
\begin{enumerate}[label=INS-\arabic*]
    \item The PSS (Mobile) should be installed from Google Play Store
    \item The PSDS (Mobile) should be installed from Google Play Store
    \item Installing PSSS requires that a trained operator perform 
    the installation
\end{enumerate}

\subsection{Interoperability}
\begin{enumerate}[label=IOP-\arabic*]
    \item The PSS shall be able to exchange data with PSSS via HTTPS
    \item The PSDS shall be able to exchange data with PSSS via HTTPS
    \item The PSMS shall be able to exchange data with PSSS via HTTPS
\end{enumerate}
\pagebreak
\subsection{Performance}
\begin{enumerate}[label=PER-\arabic*]
    \item The PSSS (Web) shall take no longer than 2s when loading a page.
    \item The PSSS (Mobile) shall take no longer than 3s when loading a view. 
    \item The PSSS shall take no longer than 2 seconds when searching for 
    products.
    \item The PSSS shall take no longer than 5 seconds when the customer 
    pay for the order.
    \item The PSSS shall take no longer than 5 seconds when the customer 
    log in.
    \item The PSSS shall take no longer than 3 seconds to logout.
    \item The PSDS shall take no longer than 3 seconds to accept an order.
    \item The PSDS shall take no longer than 3 seconds to reject an order.
    
\end{enumerate}

\subsection{Reliability}
\begin{enumerate}[label=REL-\arabic*]
    \item No more than 5 orders out of 1,000 can be lost due to software errors.
    \item The PSSS shall not be down for more than 3600 consecutive seconds.
\end{enumerate}
\subsection{Robustness}
Offline means the software is running but it lose internet connections 
with the application server.

\begin{enumerate}[label=ROB-\arabic*]
    \item If PSDS goes offline, it will try to reconnect to PSMS in 
    intervals of 10 seconds.
    \item If a message is sent from PSDS to PSSS and PSDS is offline, PSDS is 
    going to store the message in a queue and send the message 
    when it reconnects.
\end{enumerate}

\pagebreak
\begin{enumerate}[resume, label=ROB-\arabic*]
    \item If a message is sent from PSS to PSSS and PSS is offline, PSS is 
    going to store the message in a queue and send the message 
    when it reconnects.
    \item PSDS, PSS, PSMS shall have empty input fields by default and display 
    an error message in case a required input field is empty.
\end{enumerate}



\subsection{Usability}
Supported OAuth accounts: Google, Facebook, Apple. \newline
 
\noindent For the context of usability a workflow is going to be any combination of 
views, buttons, actions and inputs that helps a user to achieve a goal.

\begin{enumerate}[label=USE-\arabic*]
    \item A first time user of PSS shall be able to create an order, with a 
    cart already filled, in no longer than 3 seconds
    \item A first time user of PSS shall be able to sign up in no longer 
    than 2 minutes
    \item A first time user of PSS shall be able to sign up in no longer 
    than 20 seconds, if the user have a supported OAuth account
    \item A first time user of PSS shall be able to sign in no longer 
    than 5 seconds
    \item A first time user of PSS shall be able to sign in no longer 
    than 3 seconds, if the user have a supported OAuth account
    \item A first time user of PSS shall be able to search for an item and 
    add it to the cart in no longer than 20 seconds
    \item A first time user of PSDS shall be able to sign in no longer 
    than 5 seconds
    \item A first time user of PSDS shall be able to accept an order in no 
    longer than 10 seconds
\end{enumerate}
\pagebreak
\begin{enumerate}[resume, label=USE-\arabic*]
    \item A first time user of PSDS shall be able to deny an order in no 
    longer than 10 seconds
    \item A first time user of PSDS shall be able to logout in no longer 
    than 5 seconds
    \item A first time user of PSDS shall be able to mark that it’s on its 
    way to the merchant store, in no longer than 3 seconds
    \item A first time user of PSDS shall be able to mark that it’s on its 
    way to the costumer, in no longer than 3 seconds
    \item A first time user of PSMS shall be able to add a new product in 
    no longer than 2 minutes.
    \item A first time user of PSMS shall be able to remove a product in 
    no longer than 15 seconds.
    \item A first time user of PSMS shall be able to update a product in 
    no longer than 1 minute
    \item A first time user of PSMS shall be able to login in no longer 
    than 5 seconds
    \item A first time user of PSMS shall be able to logout in no longer 
    than 5 seconds
    \item A single workflow would be consider user-friendly as long as the 
    user makes 4 mistakes or less out of 100 times repeating the same workflow. 
    \textit{A mistake is any action that the user performs that he didn’t 
    intent to (E.g. Button miss clicks, invalid characters on input fields, 
    wrong text format)}
    \item For the systems PSMS, PSS, PSDS, 98\% of first time users should be 
    able to use the applications without needing any help.
    \item A user of PSS should be able to create an order from an already 
    filled car in no more than 4 interactions
    \item A user of PSS should be able to create an order from an empty cart 
    in no more than 8 interactions. For an order of a single item.
\end{enumerate}
\pagebreak
\begin{enumerate}[resume, label=USE-\arabic*]
    \item A user of PSDS should be able to complete a delivery in no more 
    than 2 interactions
    \item A user of PSDS should be able to signal a customer that it’s on its 
    way to the store in no more than 2 interactions
    \item A user of PSDS should be able to signal a customer that it’s on its
    way to the complete the order in no more than 2 interactions
    \item A user of PSMS should be able to add a product in no more 
    than 2 interactions
    \item A user of PSMS should be able to update a product in no more 
    than 2 interactions
    \item A user of PSS should be able to edit their own profile in no more 
    than 2 interactions
    
\end{enumerate}

\subsection{Efficiency}
\begin{enumerate}[label=EFF-\arabic*]
    \item The PSSS should have at least 30\% of processor capacity and memory 
    available to the application shall be un-usued at the planned 
    peak load conditions
\end{enumerate}

\subsection{Modifiability}
\begin{enumerate}[label=MOD-\arabic*]
    \item Classes must follow the SOLID principles
    \item Functions calls required at least 80\% of testing code coverage
    \item Public functions must be above protected functions
    \item Protected functions must be above private functions
    \item All merges to master must come from the CI server
    \item All test must pass before pushing changes to the remote repository
    \item All changes push to a release branch must be peer-reviewed.
    \item Public and protected functions must include a comment that explains 
    the functionality
\end{enumerate}
\pagebreak
\begin{enumerate}[resume, label=MOD-\arabic*]
    \item Variable must be descriptive in nature, abbreviations must be avoided
    \item Constants must be all uppercase, if the constant have more than one 
    word they would be separated by an underscore
    \item Functions and variables must begin with a lower case
    \item Classes will be capitalize
    \item Variables and functions must be written in camel case
    \item Composition must be preferred over inheritance
    \item Lines would not exceed more than 80 characters, including white 
    spaces
    \item Code format should be applied before committing
\end{enumerate}

\subsection{Portability}
\begin{enumerate}[label=POR-\arabic*]
    \item Modifying the Android version to the latest version shall require 
    changing no more than 5\% of the source code
    \item PSMS, PSS (Web) shall support:
    \begin{itemize}
        \item Chrome 89, 88, 87
        \item Latest version of Safari
        \item Firefox 87, 86, 85
        \item Microsoft Edge 89, 88, 87
    \end{itemize}
    \item PSDS, PSS (Mobile)
    \begin{itemize}
        \item Android 12, 11, 10
    \end{itemize}
\end{enumerate}
\pagebreak
\subsection{Reusability}
\begin{enumerate}[label=REU-\arabic*]
    \item Web components must be reused between PSS (Web) and PSMS.
    \item Authentication mechanism must be shared between PSS (Mobile) and PSDS
    \item At least 45\% of application architecture shall be reused 
    between PSS (Mobile) and PSDS.
    \item 2FA (2-Factor Authentication) mechanism shall be shared across 
    all the systems
    \item JWT token signing and token rotation mechanism shall be shared 
    across all the systems
\end{enumerate}

\subsection{Scalability}
\begin{enumerate}[label=SCA-\arabic*]
    \item The system should scale up the system horizontally, if the system 
    gets 95\% of CPU or RAM utilized, which ever comes first. The system will 
    spin up 2 servers with the same operating system and environment 
    but with 80\% less memory than the original server.
    \item The system will scale down to 1 (original server) if the one of the 
    previous spin up server, has less than 95\% of CPU usage during 3600 
    consecutive seconds.
\end{enumerate}

\subsection{Verifiability}
\begin{enumerate}[label=VER-\arabic*]
    \item The staging environment configuration shall be identical to the 
    production configuration environment to avoid irreproducible 
    testing failures.
    \item A tester shall be able to configure if the application is 
    running in testing, develop or production mode
\end{enumerate}
\pagebreak
\subsection{Constraints}
\begin{enumerate}[label=CON-\arabic*]
    \item Developers can only use open source libraries or tools that are 
    either Apache or MIT license.
    \item Google Pay and Apple Pay are the only supported payment providers
    \item The data interchange format must be JSON
    \item The authentication/authorization mechanism between applications 
    is going to be JWT
    \item JWT tokens are going to expired after 24 hours
    \item The database that is going to be used in the project must be MySQL
\end{enumerate}
\pagebreak