\section{Operational Scenarios}

\subsection{Checkout Scenario}
\begin{itemize}
	\item The customer approaches the self-checkout system and starts 
    the checkout process.
	\item The system initializes the cart properly, allowing the user to 
    scan and add items to the checkout list.
    \item \textbf{Items Without a Barcode (eg. fresh produce) or 
    Barcode Cannot Be Scanned}
    \begin{itemize}
        \item For these items, the user will use a built-in search 
        function in the system.
        \item The user will search for their item in the inventory manually.
        \item Once they find their item, they will manually input the number 
        of that item that they wish to add to their checkout and add it.
        \item Exception
        \begin{itemize}
            \item If the user cannot find their item through the system, 
            they will indicate this to the system.
            \item The system will then alert a trained worker to the issue
        \end{itemize}
    \end{itemize}
    \item The user scans their item and for every item scanned, the system 
    checks the store’s inventory for what item is associated with 
    the scanned barcode.
    \item The system finds the item and adds the item to the checkout, 
    signaling the user to add that item to the bagging area and to proceed
    with scanning their other items.
    \item \textbf{Exception - Item Cannot Be Found}
    \begin{itemize}
        \item The system cannot find an item in the store’s inventory with the 
        barcode read in the scanner. 
        \item It signals the user that the item scanned was not recognized by 
        the scanner as an item. It also informs the user that the item was 
        either not scanned properly or that the item does not belong 
        in the cart.
        \item The system will allow the user to rescan the item.
        \item Exception
        \begin{itemize}
            \item If the user rescans multiple times (number of rescans at 
            administrators choice) without success, the system will 
            lock and alert a trained worker to the problem.
            \item The system will unlock until the trained worker 
            unlocks the system (See Unlock Scenario).
        \end{itemize}
    \end{itemize}
    \item The system repeats the process until the user ends their 
    checkout to proceed to payment. 
    \item \textbf{User Wishes to Remove an Item from Checkout}
    \begin{itemize}
        \item The user will indicate to the system that they wish to 
        remove an item from checkout.
        \item The system will lock the scanner and then prompt the user to 
        select which item or items that the user wishes to remove.
        \item The user will indicate to the system which item and how much of 
        the item they wish to remove, and the system will remove the item 
        from checkout.
        \item Note: The system will actively prevent the user from inputting a 
        number greater than the amount of the item present in the checkout as 
        well as one less than 0.
        
        \item Exception
        \begin{itemize}
            \item If the system receives a number greater than the amount of 
            the item present in the checkout or a number less than 0, the 
            system will lock and alert a trained worker.
            \item The system will remain locked until unlocked by a trained 
            worker, system maintenance personnel, or any other authorized 
            personnel (See Unlock Scenario).
        \end{itemize}
        \item The system will then resume the normal scan scenario.
    \end{itemize}
    \item \textbf{User Wishes to Cancel Their Checkout}
    \begin{itemize}
        \item The user will indicate to the system that they wish to cancel 
        their checkout.
        \item The system will prompt the user to confirm that they wish 
        to do so.
        \item If the user confirms, then the system will prompt an employee 
        to come and collect the items the user had already scanned 
        and not scanned.
    \end{itemize}
    \item When the user wishes to checkout, they will prompt the system to 
    end the scanning process.
    \item The system will lock the scanner and prompt the user to choose a 
    payment method of either cash, debit, or credit.
    \item \textbf{Cash}
    \begin{itemize}
        \item The system will start the hardware to receive the currency. 
        The system will prompt the user to insert the appropriate bills and 
        coins to fulfill the cost of the checkout.
        \item The user inserts the currency into the hardware for counting. 
        The system will continue to prompt the user with the remaining cost 
        of the cart until the amount inserted is at least equal to the 
        total cost.
        \item {\it User Inserts More Than The Cost}
        \begin{itemize}
            \item The system will indicate to the user that they will receive 
            change from the coin and bill slots on the hardware. The system 
            will indicate to the internal currency register how much must be 
            taken out for change,
            \item The system withdraws from the register to give to the user.
        \end{itemize}
    \end{itemize}
    \item \textbf{Debit and Credit}
    \begin{itemize}
        \item The system will prompt the user to follow the instructions 
        presented on card terminal.
        \item The system communicates with the terminal as for how much the 
        user needs to pay to cover the cost.
        \item The terminal carries out the transaction, where the user swipes 
        their credit card or inserts their debit card.
        \item Exception - Card Declined
        \begin{itemize}
            \item The system will indicate to the user that their card 
            was declined.
            \item The system will then prompt the user to choose their payment 
            method again. This process will repeat until the user cancels 
            their checkout or the user covers the cost.
        \end{itemize}
    \end{itemize}
    \item Once the transaction is completed, the system will print a receipt 
    for the user of their checkout list and end the checkout process.
    \item The system will reset itself for another user.
\end{itemize}

\subsection{Unlock Scenario}
\begin{itemize}
    \item This scenario occurs when the system locks during an error during 
    the checkout scenario.
    \item Once the system alerts a trained worker to the error, the trained 
    worker will approach the system to assist the user.
    \item Once the worker assesses the problem and decides that it is good to 
    proceed with the checkout scenario, the worker will input a special code 
    that they will be given by system maintenance personnel. This code will 
    automatically unlock the system for continued use by the user or the worker 
    depending on the decision made by the worker.
    \item This special code will be accessible to system maintenance personnel, 
    administrative personnel, and the trained workers assigned to the 
    system units.
\end{itemize}

\subsection{Shutdown Scenario}
\begin{itemize}
    \item This scenario occurs when it is the end of the day and the store is 
    closing for the night and the system units are not in use.
    \item A trained worker or administrator who is present at the time of 
    closing will cancel any current checkout processes that are present on 
    the system units.
    \item The trained worker will indicate to the system that they wish to 
    shutdown the unit.
    \item The system will prompt the worker to provide their special 
    code to the system.
    \item The worker provides their special code to the system.
    \item If the code check outs, the system will shut down.
\end{itemize}

\subsection{Maintenance Scenario}
\begin{itemize}
    \item This scenario occurs when the system requires some hardware or 
    software maintenance.
    \item System maintenance personnel, or IT, will have access to a key to 
    open the unit to expose its hardware as well as their own code separate 
    from the one provided to trained workers.
    \item \textbf{System Not Yet Ready for Maintenance}
    \begin{itemize}
        \item IT will prompt the unit to receive their IT code. If code does 
        not work, see Special Code Error Scenario.
        \item The system will receive the code and go into a complete 
        lockdown, terminating all processes.
    \end{itemize}
    \item IT will open the unit and expose the hardware of the system unit, 
    including a port into the system’s software for all software maintenance 
    as well as a system reboot button.
    \item IT will then conduct all required maintenance on the unit.
    \item Once maintenance is complete, IT will remove all equipment or any 
    other items that do not belong in the unit. They will also remove their own 
    machine from the unit’s software port if software maintenance was required.
    \item IT will press the reboot button in the unit for the system to return 
    to normal operations.
    \item It will close and lock the unit shut, protecting the hardware again.
\end{itemize}

\subsection{Special Code Error Scenario}
\begin{itemize}
    \item This scenario occurs when a user attempts to provide the system with 
    a special code but the system does not recognize the given code as a 
    special one.
    \item The system will prompt the user that the code is incorrect and to 
    input the special code.
    \item This process repeats until a correct special code is provided.
    \item Multiple Incorrect Attempts
    \begin{itemize}
        \item After multiple incorrect attempts (the exact number of which is 
        up to administration or system maintenance personnel), the system will 
        completely lock, terminating all current processes, and will require 
        system maintenance.
    \end{itemize}
\end{itemize}
