\section{Key Stakeholders}

\subsection{Merchants}
The major benefits that the merchants will receive from the application are to 
increase their exposure, while also saving cost because they wouldn't need to 
hire a delivery service nor there is a need to keep maintenance 
of the vehicles.\newline

\noindent One of the major features is that the application will provide the 
merchant a delivery service, a bigger pool of customers while also enables 
insights on what customers are purchasing, giving them information on what 
items to promote.\newline

\noindent The merchants that the application is going to target are small 
stores and boutiques, one of their constraints is that they are short staff so 
they can't have a dedicated person to handle the picking up the items, and we 
don’t want to be intrusive in their workflow so the drivers will do the 
shopping and pick up the items like an everyday customer.

\subsection{Customers}
The major benefits for customers are that they will be able to find out 
merchants near their home from where they can purchase, since the merchants 
that get a display in the user's app, are close to the customers, the delivery 
time is fast. \newline

\noindent Customers also avoid spending time going to the stores, doing the 
line, and purchasing the items, they only need to make the order and they get 
it delivered to their doorstep in less than 2 hours.

\subsection{Developers}
The developers belong to the same company as the requirement engineering team, 
for them, the main concern is clear, precise, and verifiable requirements.

\subsection{Drivers}
The main benefit for the drivers is to get another source of income by using 
their current means of transportation as an asset. \newline

\noindent For them, one of the major features is going to display in the map 
the place where they need to do the shopping and the location where they need 
to deliver. \newline

\noindent They also require to keep track of the milage and time of the order, 
and also keep track of all the orders that they delivered.

