\section{Key Drivers}
\subsection{Small Businesses}
The reason that we are building this application is to help small 
businesses to compete with the big stores. Because of COVID small businesses 
are now forced to migrate their operations online. Big companies like Amazon 
and Shopify were online since the beginning, Walmart, Target and BestBuy 
have their main operations in store but they also had an online 
presence. \newline

\noindent Since these companies already have their own delivery service, 
they are now focusing on improving and refining their e-commerce experience. 
This puts small businesses in a peril, since they already work with small 
profit margins to begin with, they lack the capital to hire the technical 
skills required to create an online presence. \newline

\subsection{Unemployment}
\noindent Not only small businesses are affected, since the beginning of 
the pandemic unemployment has been rising, particularly in the US. That’s why 
this application does not only help small businesses but also helps people 
who have their own method of transportation and want to make extra money 
by fulfilling orders from the platform.\newline

\noindent This application will help small businesses and people without jobs 
while also helping to keep social distancing during the pandemic, 
now people more than ever are ordering online, so this is a good opportunity 
for a new player to get into the market.

\subsection{Health Risk}
\noindent Since the begining of the pandemic, stores are required to shutdown 
or limit the amount of people they can have inside the stores, which translates 
into less sales for the merchants. Going to the store also increase the 
customer exposure to the virus. \newline

\noindent With the application we can reduce the amount of people inside the 
stores while also helping the businesses to keep their sales.

\pagebreak

\subsection{Convenience}
\noindent We want to enable our customers to have the same experience that 
they receive while ordering fast-food. For this reason we want to create 
an application that makes the purchase experience as seamless as possible.