\section{Key Constraints}
\subsection{Business Constraints}
\begin{enumerate}[label=CON-\arabic*]
    \item Drivers are required to have a background check before being 
    apply to be enroll in the platform.
    \item Business are required to provide their opening and closing hours.
    \item Drivers must have their own vehicle, transportation insurance and 
    health insurance.
    \item Drivers must be over 18 years old.
    \item Merchants must have a business license.
\end{enumerate}
\subsection{Project Constraints}
\begin{enumerate}[resume, label=CON-\arabic*]
    \item Developers can only use open source libraries or tools that are 
    either Apache or MIT license.
    \item Google Pay, Apple Pay and PayPal are the only supported payment 
    providers.
    \item The data interchange format must be JSON.
    \item The authentication/authorization mechanism between applications 
    is going to be JWT.
    \item JWT tokens are going to expired after 24 hours.
    \item The database that is going to be used in the project must be MySQL.
    \item There is only one driver per session. \textit{A driver can't login 
    in two devices at the same time.}
    \item PSSS will only accept orders from the merchant opening hour to 60 
    minutes before the merchant closing time.
    \item Merchants are only going to be displayed to customers if they are 
    less than 2 miles from each outer.
    \item All application must follow Google Material Design 
    guidelines \cite{material-design-guidelines}.
    \item Images should take less than 10MB.
\end{enumerate}