\documentclass[12pt]{article}
\def\arraystretch{1.2}%
\usepackage[a4paper,
	bindingoffset=0.2in,%
        left=1.2in,
        right=1.2in,
        top=1in,
        bottom=0.5in,%
        footskip=.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{xltxtra,fontspec,xunicode}
\setromanfont[Numbers=Uppercase]{Inter}
\defaultfontfeatures{Scale=MatchLowercase}

{
    \fontfamily{lmss}\selectfont 

    %opening
    \title{
       Personalized Shopping Assistant  \\ 
        \small Team 4
    }

    \author{
        Thomas Ripp
        \and 
        Joseph Mirabile
        \and 
        Jose Cruz
    }

    \date{
        Stevens Institute of Technology \\
        \small\today
    } 

    \begin{document}
    \maketitle
    \tableofcontents
    \pagebreak
}

\section{Mission Statement}
For the people who are busy and enjoy purchasing online, that requires their products delivered to their doorstep as fast as possible, the shopping assistant is the fastest and most reliable platform, unlike Shopify or Amazon that takes multiple days to deliver your products, our product offers a vast catalog of products, from your nearby stores, so you can buy from your favorite stores without leaving the house.

\pagebreak

\section{Key Drivers}
\subsection{Small Businesses}
The main reason that we are building this application is to help small businesses to compete with the big stores. Because of COVID small businesses are now forced to migrate their operations online. Big companies like Amazon and Shopify were online since the beginning, Walmart, Target and BestBuy have their main operations in store but they also had an online presence. \newline

\noindent Since these companies already have their own delivery service, they are now focusing on improving and refining their e-commerce experience. This puts small businesses in a peril, since they already work with small profit margins to begin with, they lack the capital to hire the technical skills required to create an online presence. \newline

\subsection{Unemployment}
\noindent Not only small businesses are affected, since the beginning of the pandemic unemployment has been rising, particularly in the US. That’s why this application does not only help small businesses but also helps people who have their own method of transportation and want to make extra money by fulfilling orders from the platform.\newline

\noindent This application will help small businesses and people without jobs while also helping to keep social distancing during the pandemic, now people more than ever are ordering online, so this is a good opportunity for a new player to get into the market.

\pagebreak

\section{Key Constraints}
\subsection{Competition}
Even though it's a good opportunity for a company to enter the e-commerce/delivery market, because of the current world condition, is also a problem because there are large companies already settled in the market, our direct competitor would be Postmates (owned by Uber). Postmates do not have a lot of variety of products, at least in Hoboken, but since they are backed by Uber they already have the technology, capital and talent on their side to improve their offering. \newline

\subsection{Fast product market fit}
\noindent The company will focus on delivering a good customer experience to get customer loyalty, but this needs to happen as soon as possible before the competition takes notice and begins to adapt to our strategy. We need to get good relationships not only with our customers but also with the stores to help us decrease the delivery time as much as possible \newline

\subsection{Parking}
\noindent Another constraint is that in Hoboken it is difficult to get a parking spot in stores so this will increase the delivery time, we are planning to overcome this by getting deals with the store for a faster checkout process. Since e-commerce is a competitive market and the application is handling not only personal information but also money, the application needs to work well from the beginning while also comply with all the regulations and laws. \newline

\pagebreak

\subsection{Drivers}
\noindent Regarding the drivers since we are just starting we can’t pay for the drivers car insurance or expenses, they would have to come with their own insurance and their own background check, because customer service is specially important to the company. Besides the business and infrastructure expenses the company also needs to focus on creating a good customer service experience.\newline

\subsection{Items Size}
\noindent From the stores we will add a constraint regarding size and weight, they can’t publish items that can not fit inside a car or are too heavy to be carried.


\end{document}